---
title: "draft sheet"
author: "Andy Krause"
date: "March 20, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
 
```{r, echo=FALSE}
  library(magrittr)
  load(file = file.path('C:/Code/sportsQuant/FBB30x30', 'output', 'fordraft.rdata'))
```

## Team Tiers

| Tier 1 | Tier 2 | Tier 3 | Tier 4 |
| :-----: | :-----: | :-----: | :------: |
| BOS   | STL   | OAK...   | SF...   |
| CLE   | ATL   | PIT...   |  CWS...   |
| NYY   | MIL   | TB   | MIA   |
| PHI    | CHC   | TEX   | BAL   |
| WSH   | ...CIN    | ARI   | DET   |
| HOU   | ...MIN   | LAA   |   |
| LAD   | ...NYM   |...KC   |   |
| COL    | ...TOR      | ...SEA   |   |
 | | ...SD | |   

## Team Fill In

| Team | Player | | Team | Player | | Team | Player |
| :-----: | :-------------------: | :-----: | :-------------------: | :-----: | :-------------------: |
|     |   |     | |     | |
| BAL | __________________ | CWS | ___________________ | HOU | _______________ |
|     |   |     | |     | |
| BOS | __________________  | MIN | ___________________ | LAA | _______________ |
|     |   |     | |     | |
| NYY | __________________  | KC  | ___________________| OAK | _______________ |
|     |   |     | |     | |
| TB  | __________________  | CLE | ___________________| SEA |  _______________|
|     |   |     | |     | |
| TOR | __________________  | DET | ___________________| TEX | _______________ |
|     |   |     | |     | |
| PHI | __________________  | MIL | ___________________| SF  | _______________ |
|     |   |     | |     | |
| ATL | __________________  | STL | ___________________| LAD | _______________ |
|     |   |     | |     | |
| NYM | __________________  | CIN | ___________________| SD  | _______________ |
|     |   |     | |     | |
| WSH | __________________  | PIT | ___________________| COL | _______________ |
|     |   |     | |     | |
| MIA | __________________  | CHC | ___________________| ARI | _______________ |
|     |   |     | |     | |

\pagebreak

## Hold Targets

* **ARI**: Bradley/Hirano
* **DET**: Jimenez
* **HOU**: Pressly
* **MIA**: Romo/Steckenrider
* **PIT**: Kela
* **SD**: Stammen/Wintgenter
* **SF**: Watson/Dyson/Smith/Melancon
* **TB**: Roe/Castillo
* **TEX**: Chavez
* **TOR**: Tepera

## Sleeper Targets

* F. Meija - C - SD
* V. Robles - OF - WSH
* W. Adames - 2B/SS - TOR
* L. Gurriel - 2B/SS - TOR
* B. Lowe - 2B - TB
* J. Candelario - 3B - DET
* C. Pinder - 1B/2B - OAK
* M. Pineda - SP - MIN
* C. Paddack - SP - SD
* M. Strahm - SP - SD
* F. Peralta - SP - MIL
* B. Woodruff - SP - MIL
* E. Lauer - SP - SD
* J. Luchesi - SP - SD
* T. Richards - SP - MIA
* B. Keller - SP - KC
* C. Smith - SP - MIA
* P. Lopez - SP - MIA


\pagebreak
 
## Catchers

```{r, echo=FALSE}
  knitr::kable(bpos[['C']] %>% dplyr::select(-c(adp, pos)) %>%
                 dplyr::mutate(player = substr(player, 1, 17)))
```

\pagebreak

\pagebreak

## 1B
```{r, echo=FALSE}
  knitr::kable(bpos[['1B']] %>% dplyr::filter(rrv > -.82)  %>% dplyr::select(-c(adp, pos)) %>%
                 dplyr::mutate(player = substr(player, 1, 17)))
```

\pagebreak

## 2B
```{r, echo=FALSE}
  knitr::kable(bpos[['2B']] %>% dplyr::filter(rrv > -1)  %>% dplyr::select(-c(adp, pos)) %>%
                 dplyr::mutate(player = substr(player, 1, 17)))
```

\pagebreak

\pagebreak

## SS
```{r, echo=FALSE}
  knitr::kable(bpos[['SS']] %>% dplyr::filter(rrv > -1) %>% dplyr::select(-c(adp, pos)) %>%
                 dplyr::mutate(player = substr(player, 1, 17)))
```

\pagebreak

## 3B
```{r, echo=FALSE}
  knitr::kable(bpos[['3B']] %>% dplyr::filter(rrv > -.9)  %>% dplyr::select(-c(adp, pos)) %>%
                 dplyr::mutate(player = substr(player, 1, 17)))
```

\pagebreak

\pagebreak

## LF
```{r, echo=FALSE}
  knitr::kable(bpos[['LF']] %>% 
                 dplyr::filter(rrv > -.29) %>% 
                 dplyr::select(-c(adp, pos)) %>%
                 dplyr::mutate(player = substr(player, 1, 17)))
```

\pagebreak

\pagebreak

## CF
```{r, echo=FALSE}
  knitr::kable(bpos[['CF']] %>% dplyr::filter(rrv > -.97) %>% dplyr::select(-c(adp, pos)) %>%
                 dplyr::mutate(player = substr(player, 1, 17)))
```

\pagebreak

\pagebreak

## RF
```{r, echo=FALSE}
  knitr::kable(bpos[['RF']] %>% dplyr::filter(rrv > -.33)  %>% dplyr::select(-c(adp, pos)) %>%
                 dplyr::mutate(player = substr(player, 1, 17)))
```

\pagebreak

## DH
```{r, echo=FALSE}
  knitr::kable(bpos[['DH']] %>% dplyr::filter(rrv > -1)  %>% dplyr::select(-c(adp, pos)) %>%
                 dplyr::mutate(player = substr(player, 1, 17)))
```

\pagebreak

## SP
```{r, echo=FALSE}
  knitr::kable(ppos[['SP']] %>% dplyr::filter(rrv > -1)  %>% dplyr::select(-c(adp, pos)) %>%
                 dplyr::mutate(player = substr(player, 1, 17)))
```


\pagebreak

## RP
```{r, echo=FALSE}
  knitr::kable(ppos[['RP']] %>% dplyr::filter(rrv > -.74)  %>% dplyr::select(-c(adp, pos)) %>%
                 dplyr::mutate(player = substr(player, 1, 17)))
```

\pagebreak
\pagebreak

```{r}
  knitr::kable(full_df[1:350, ])

```

\pagebreak
\pagebreak

```{r}
i <- 1
knitr::kable(team_[[i]], format = 'latex')
i <- i + 1
```

```{r}
knitr::kable(team_[[i]], format = 'latex')
i <- i + 1
```

\pagebreak

```{r}
knitr::kable(team_[[i]], format = 'latex')
i <- i + 1
```

```{r}
knitr::kable(team_[[i]], format = 'latex')
i <- i + 1
```

\pagebreak

```{r}
knitr::kable(team_[[i]], format = 'latex')
i <- i + 1
```

```{r}
knitr::kable(team_[[i]], format = 'latex')
i <- i + 1
```
\pagebreak

```{r}
knitr::kable(team_[[i]], format = 'latex')
i <- i + 1
```

```{r}
knitr::kable(team_[[i]], format = 'latex')
i <- i + 1
```
\pagebreak

```{r}
knitr::kable(team_[[i]], format = 'latex')
i <- i + 1
```

```{r}
knitr::kable(team_[[i]], format = 'latex')
i <- i + 1
```
\pagebreak

```{r}
knitr::kable(team_[[i]], format = 'latex')
i <- i + 1
```

```{r}
knitr::kable(team_[[i]], format = 'latex')
i <- i + 1
```
\pagebreak

```{r}
knitr::kable(team_[[i]], format = 'latex')
i <- i + 1
```

```{r}
knitr::kable(team_[[i]], format = 'latex')
i <- i + 1
```
\pagebreak

```{r}
knitr::kable(team_[[i]], format = 'latex')
i <- i + 1
```

```{r}
knitr::kable(team_[[i]], format = 'latex')
i <- i + 1
```
\pagebreak

```{r}
knitr::kable(team_[[i]], format = 'latex')
i <- i + 1
```

```{r}
knitr::kable(team_[[i]], format = 'latex')
i <- i + 1
```
\pagebreak

```{r}
knitr::kable(team_[[i]], format = 'latex')
i <- i + 1
```

```{r}
knitr::kable(team_[[i]], format = 'latex')
i <- i + 1
```
\pagebreak

```{r}
knitr::kable(team_[[i]], format = 'latex')
i <- i + 1
```

```{r}
knitr::kable(team_[[i]], format = 'latex')
i <- i + 1
```
\pagebreak

```{r}
knitr::kable(team_[[i]], format = 'latex')
i <- i + 1
```

```{r}
knitr::kable(team_[[i]], format = 'latex')
i <- i + 1
```
\pagebreak

```{r}
knitr::kable(team_[[i]], format = 'latex')
i <- i + 1
```

```{r}
knitr::kable(team_[[i]], format = 'latex')
i <- i + 1
```
\pagebreak

```{r}
knitr::kable(team_[[i]], format = 'latex')
i <- i + 1
```

```{r}
knitr::kable(team_[[i]], format = 'latex')
i <- i + 1
```
\pagebreak

```{r}
knitr::kable(team_[[i]], format = 'latex')
i <- i + 1
```

```{r}
knitr::kable(team_[[i]], format = 'latex')
i <- i + 1
```
