---
title: "1_Update_Data"
author: "Andy Krause"
date: "3/6/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

This is the file to run through, manually, each year prior to running any analyses or simulations.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Setup

Set the upcoming year

```{r}
  YEAR <- 2020
```

Load Libraries

```{r comment = FALSE, message = FALSE, warning = FALSE}
  library(readr)
  library(tidyverse)
  library(FBB30x30)
```

Set the names of the tables from Baseball Reference that you'll need to read from for the statistics.  It is highly unlikely you'll need to change this, unless you change scoring categories. Consult www.baseballreference.com for details on the available tables.  

```{r}

  baseballref_df <- data.frame(data = c('Batting - Standard', 'Batting - Ratio',
                                        'Batting - Value', 'Batting - Pitches',
                                        'Batting - Win Probability', 'Batting - Advanced', 
                                        'Batting - Situational', 'Batting - Baserunning', 
                                        'Fielding - Appearances', 'Fielding - Standard',
                                        'Pitching - Standard', 'Pitching - Starter',
                                        'Pitching - Reliever', 'Pitching - Ratio',
                                        'Pitching - Value', 'Pitching - Pitches', 
                                        'Pitching - Win Probability'),
                               code = c('standard-batting', 'ratio-batting', 
                                        'value-batting', 'pitches-batting', 
                                        'win_probability-batting', 
                                        'advanced-batting', 'situational-batting',
                                        'baserunning-batting', 
                                        'appearances-fielding', 
                                        'standard-fielding', 'standard-pitching',
                                        'starter-pitching', 'reliever-pitching',
                                        'ratio-pitching', 'value-pitching',
                                        'pitches-pitching', 
                                        'win_probability-pitching'),
                               stringsAsFactors = FALSE) %>%
    tibble::as.tibble()
  usethis::use_data(baseballref_df, overwrite=TRUE)
  
```

### Standard Lahman Data 

Next, downlad the new **players.csv** file from Lahman database.  In recent years this was only available at https://github.com/chadwickbureau/baseballdatabank in .csv.  Ensure the formatting is correct before proceeding.  

```{r eval=FALSE}

  # Read in file of new players
  setwd('..')
  players_df <- readr::read_delim(file = file.path(getwd(), 'data', 'raw', 
                                                    'players', 'people.csv'), delim = ',')

  # Prepare data
  players_df <- players_df %>%
    dplyr::filter(as.Date(as.character(finalGame)) >= as.Date('2014-01-01')) %>%
    dplyr::select(player_id = playerID, retro_id = retroID, bbref_id = bbrefID, 
                  first = nameFirst, last = nameLast, given = nameGiven, 
                  last_game = finalGame) %>%
    dplyr::mutate(full = paste(first, last),
                  last_game = as.Date(as.character(last_game)),
                  player_id = as.character(player_id), 
                  retro_id = as.character(retro_id), 
                  bbref_id = as.character(bbref_id), 
                  first = as.character(first), 
                  last = as.character(last), 
                  given = as.character(given))
  class(players_df) <- c('players', class(players_df))
  
  ## Save object
  usethis::use_data(players_df, overwrite=TRUE)

```

Update the teams.  This is very unlikely to change year to year, but it is easy to do.  Like the players, download **teams.csv** from a Lahman source. 

```{r, eval = FALSE}
  
  # Read in data
  setwd('..')
  teams_df <- readr::read_delim(file.path(getwd(), 'data', 'raw', 'players', 'teams.csv'),
                                delim = ',')
  
  # Prepare Data
  teams_df <- teams_df %>%
    dplyr::filter(yearID == YEAR - 1) %>%
    dplyr::select(team_id = teamID, br_id = teamIDBR, lahman_id = teamIDlahman45,
                  retro_id = teamIDretro) %>%
    dplyr::mutate(espn_id = c('ARI', 'ATL', 'BAL', 'BOS', 'CWS', 'CHC', 'CIN', 'CLE',
                              'COL', 'DET', 'HOU', 'KC', 'LAA', 'LAD', 'MIA', 'MIL',
                              'MIN', 'NYY', 'NYM', 'OAK', 'PHI', 'PIT', 'SD', 'SEA',
                              'SF', 'STL', 'TB', 'TEX', 'TOR', 'WAS'),
                  retrosheet_id = c('ARI N', 'ATL N', 'BAL A', 'BOS A', 'CHI A', 'CHI N',
                                    'CIN N', 'CLE A', 'COL N', 'DET A', 'HOU A', 'KC  A', 
                                    'ANA A', 'LA  N', 'MIA N', 'MIL N', 'MIN A', 'NY  A',
                                    'NY  N', 'OAK A', 'PHI N', 'PIT N', 'SD  N', 'SEA A',
                                    'SF  N', 'STL N', 'TB  A', 'TEX A', 'TOR A', 'WAS N'))
  class(teams_df) <- c('teams', class(teams_df))

  # Save Object
  usethis::use_data(teams_df, overwrite=TRUE)
```

### Load Baseball Reference Stats 

Begin by loading the fielding stats for the most recent year and combining them with those from prior years.  The `getBRStats()` function does the scraping. 

```{r, eval = FALSE}
  
  # Load existing data
  data(fielding_df, package = 'FBB30x30')
  fielding_df <- fielding_df %>% 
    dplyr::filter(year != YEAR)

  # Read in Fielding data
  fielding_df <- purrr::map(.x = YEAR - 1,
                            .f = getBRStats,
                            type ='fielding') %>%
    dplyr::bind_rows(., fielding_df) %>%
    dplyr::distinct(player_id, year, .keep_all = TRUE)
  
   usethis::use_data(fielding_df, overwrite=TRUE)

```

Next, load the batting stats for the most recent year and combining them with those from prior years.  The `getBRStats()` function does the scraping. 

```{r, eval = FALSE}
   
  # Load existing data
  data(batting_df, package = 'FBB30x30')
  batting_df <- batting_df %>% 
    dplyr::filter(year != YEAR)

  # Load Data
   batting_df <- purrr::map(.x = YEAR - 1,
                            .f = getBRStats,
                            type ='batting') %>%
     dplyr::bind_rows(., batting_df) %>%
    dplyr::distinct(player_id, year, .keep_all = TRUE)
   
   usethis::use_data(batting_df, overwrite=TRUE)

```

Then load the pitching stats for the most recent year and combining them with those from prior years.  The `getBRStats()` function does the scraping. 

```{r, eval = FALSE}
  
   # Load existing data
  data(pitching_df, package = 'FBB30x30')
  pitching_df <- pitching_df %>% 
    dplyr::filter(year != YEAR)
 
  # Pitching stats
  pitching_df <- purrr::map(.x = YEAR - 1,
                            .f = getBRStats,
                            type ='pitching') %>%
     dplyr::bind_rows(., pitching_df) %>%
    dplyr::distinct(player_id, year, .keep_all = TRUE)
   
  # Save object
  usethis::use_data(pitching_df, overwrite=TRUE)
   
```

### Projections

Now we turn to projects for this year.  These are downloades manually from FantasyPros. 

Start with batting.

```{r, eval = FALSE}

  # Load Existing
  data(batprojs_df)
   batprojs_df <- batprojs_df %>% 
    dplyr::filter(year != YEAR)

  # Load New Projections
  setwd('..')
  new_hp <- read.csv(file.path(getwd(), 'data', 'raw', 'projections',
                                  paste0('fp_hitters_', YEAR, '.csv')))

  # Prep data
  names(new_hp) <- tolower(names(new_hp))
  new_hp <- new_hp %>%
      dplyr::rename(pos = positions) %>%
      dplyr::mutate(year = YEAR,
                    pos = gsub(',', '/', pos),
                    pos = gsub('/', ' | ', pos),
                    player = as.character(player),
                    team = as.character(team)) %>%
      dplyr::mutate(pos_list = strsplit(pos, ' | ')) %>%
      tidyr::unnest() %>%
      dplyr::filter(pos_list != '|') %>%
      tidyr::nest(pos_list, .key = 'pos_list') %>%
      addPlayerID(., players_df = players_df) 
    
    gidp_df <- projectGIDP(batting_df, new_hp, proj_year = YEAR)
    e_df <- projectErrors(fielding_df, new_hp, proj_year = YEAR)
    
    new_hp <- new_hp %>%
      dplyr::left_join(gidp_df, by = 'player_id') %>%
      dplyr::left_join(e_df, by = 'player_id') %>%
      tibble::as.tibble()%>%
      dplyr::select(player_id, player, team, year, pos, pos_list, 
                    tidyselect::everything())
    
    # Combine
    batprojs_df <- dplyr::bind_rows(new_hp, batprojs_df) %>%
      structure(., class = c('projections', 'batting', 'tbl_df', 'tbl', 'data.frame')) %>%
    dplyr::distinct(player_id, year, .keep_all = TRUE)
   
    # Save Object
    usethis::use_data(batprojs_df, overwrite=TRUE)

```

Then pitching

```{r, eval = FALSE}
    
  # Load Existing
  data(pitchprojs_df)
  pitchprojs_df <- pitchprojs_df %>% 
    dplyr::filter(year != YEAR)

  # Load New Projections
  setwd('..')
  new_pp <- read.csv(file.path(getwd(), 'data', 'raw', 'projections',
                                  paste0('fp_pitchers_', YEAR, '.csv')))

  # Prep Data
  names(new_pp) <- tolower(names(new_pp))
    new_pp <- new_pp %>%
      dplyr::rename(pos = positions) %>%
      dplyr::mutate(pos = gsub(',', '/', pos),
                    pos = gsub('/', ' | ', pos),
                    year = 2020,
                    player = as.character(player),
                    team = as.character(team)) %>%
      dplyr::select(-c(hr))%>%
      dplyr::mutate(pos_list = strsplit(pos, ' | ')) %>%
      tidyr::unnest() %>%
      dplyr::filter(pos_list != '|') %>%
      tidyr::nest(pos_list, .key = 'pos_list') %>%
      addPlayerID(., players_df = players_df) 
    
    qs_df <- projectQS(pitching_df, new_pp, proj_year = 2020)
    holds_df <- projectHolds(pitching_df, new_pp, proj_year = 2020)
    
    new_pp <- new_pp %>%
      dplyr::left_join(qs_df, by = 'player_id') %>%
      dplyr::left_join(holds_df, by = 'player_id') %>%
      tibble::as.tibble() %>%
      dplyr::select(player_id, player, team, year, pos, pos_list, 
                    tidyselect::everything())
      
    # Combine Al
    pitchprojs_df <- dplyr::bind_rows(new_pp, pitchprojs_df) %>%
      structure(., class = c('projections', 'pitching', 'tbl_df', 'tbl', 'data.frame')) %>%
    dplyr::distinct(player_id, year, .keep_all = TRUE)

    # Save Object
    usethis::use_data(pitchprojs_df, overwrite=TRUE) 
```

### Rankings

Same for the rankings, these are downloaded from Fantasy Pros. 

```{r, eval = FALSE}
    
  ## Load Existing Data
  data(rankings_df)
  rankings_df <- rankings_df %>% 
    dplyr::filter(year != YEAR)

  ## Read in Data  
  setwd('..') 
  new_rank <- read.csv(file.path(getwd(), 'data', 'raw', 'rankings', 
                                  paste0('fp_draftrankings_', YEAR, '.csv')))
  
  # 2020
  names(new_rank) <- tolower(names(new_rank))
  new_rank <- new_rank %>% 
    dplyr::rename(pos = positions,
                  ranking = rank,
                  st_dev = std.dev) %>%
    dplyr::mutate(pos = gsub(',', '/', pos),
                  pos = gsub('/', ' | ', pos),
                  year = YEAR,
                  team = as.character(team),
                  player = as.character(player),
                  adp = as.numeric(adp),
                  avg = as.numeric(avg)) %>%
    tibble::as.tibble() %>%
    dplyr::select(-c(vs..adp)) %>%
    tibble::as.tibble() %>%
    dplyr::mutate(pos_list = strsplit(pos, ' | ')) %>%
    tidyr::unnest() %>%
    dplyr::filter(pos_list != '|') %>%
    tidyr::nest(pos_list, .key = 'pos_list') %>%
    dplyr::select(player, team, pos, year, ranking, tidyselect::everything()) %>%
    addPlayerID(., players_df) %>%
    dplyr::select(player_id, player, year, team, pos, pos_list, ranking,
                  tidyselect::everything())
  
  # ## TEMP
  new_rank$adp[is.na(new_rank$adp)] <- ceiling(new_rank$avg[is.na(new_rank$adp)])
  
  # Combine All
  rankings_df <- dplyr::bind_rows(new_rank, rankings_df) %>%
    structure(., class = c('draftRankings', 'tbl_df', 'tbl', 'data.frame')) %>%
    dplyr::distinct(player_id, year, .keep_all = TRUE)
  
  # Save Object
  usethis::use_data(rankings_df, overwrite=TRUE) 
  
```

### Past Seasons

From our ESPN home page, download the results from the past season to a .csv file.  Be sure to the team number (gained from the URL on each manager's page.)

```{r, eval = FALSE}

  # load existing data  
  data(seasons_, package = 'FBB30x30')

  ## Read in New Data 
  setwd('..')
  new_seasons <- readr::read_delim(file.path(getwd(), 'data', 'raw', 'seasons', 
                                             paste0('season', YEAR - 1, '.csv')),
                                      delim = ';')
  
  # Pred Data
  new_seasons <- new_seasons %>%
    dplyr::select(team = Team, rank = Rank, r = R, hr = HR, rbi = RBI, so = K, sb = SB, 
                  obp = OBP, slg = SLG, gidp = GIDP, e = E, ip = IP, qs = QS, k = K_1, 
                  sv = SV, hd = HD, whip = WHIP, moves = Moves, starts = Starts) %>%
    structure(., class = c('season', class(seasons_[['2015']])))
  
  # Add to list
  seasons_[[YEAR-1]] <- new_seasons
  
  # Save object
  usethis::use_data(seasons_, overwrite=TRUE) 

```
